Tabsets

### 2024-07-09 tabsets.qmd
running
prerender

>>>>

```{r, echo=F, message=F, warning=F}
ManifoldDestiny::wasmconload()
#modlat <- eqpar$meql
#md <- ManifoldDestinyWASMD::metad
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
#metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
#mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
```

```{r}
knitr::knit_exit()
```
